rang: Reconstructing reproducible R computational environments

### 2023-03-10 paper/paper.qmd
Remove figures #111

The above code snippet can be executed with the generated container without any problem (@fig-figure1).

```{r}
#| fig.cap: The code snippet running in a R 3.5.1 container created with rang
#| echo: FALSE
#| label: fig-figure1
knitr::include_graphics("quanteda_rstudio.png", dpi = 300)
```

@@

`rang` has native support for Bioconductor packages since version 0.2. We obtained the R script `"PaperFigure.R"` from the Github repository of `Sushi` [^sushi], which generates the figure in the original paper [@phanstiel:2014:S]. Similar to the above case of `ptproc`, we made a completely automated BASH script to run `"PaperFigure.R"` and get the generated figure out of the container (@fig-figure2). We made no modification to `"PaperFigure.R"`.

@@

```{r}
#| fig.cap: The figure from the batch execution of `PaperFigure.R` inside a Docker container generated by `rang`
#| echo: FALSE
#| label: fig-figure2
knitr::include_graphics("sushi_figure1.pdf", dpi = 300)
```

>>>>

The above code snippet can be executed with the generated container without any problem `Fig~\ref{fig1}`{=latex}.

<!-- ```{r} -->
<!-- #| fig.cap: The code snippet running in a R 3.5.1 container created with rang -->
<!-- #| echo: FALSE -->
<!-- #| label: fig-figure1 -->
<!-- knitr::include_graphics("quanteda_rstudio.png", dpi = 300) -->
<!-- ``` -->

```{=tex}
% Place figure captions after the first paragraph in which they are cited.
\begin{figure}[!h]
\caption{The code snippet running in a R 3.5.1 container created with rang.}
\label{fig1}
\end{figure}
```

@@

`rang` has native support for Bioconductor packages since version 0.2. We obtained the R script `"PaperFigure.R"` from the Github repository of `Sushi` [^sushi], which generates the figure in the original paper [@phanstiel:2014:S]. Similar to the above case of `ptproc`, we made a completely automated BASH script to run `"PaperFigure.R"` and get the generated figure out of the container (`Fig~\ref{fig2}`{=latex}). We made no modification to `"PaperFigure.R"`.

@@

<!-- ```{r} -->
<!-- #| fig.cap: The figure from the batch execution of `PaperFigure.R` inside a Docker container generated by `rang` -->
<!-- #| echo: FALSE -->
<!-- #| label: fig-figure2 -->
<!-- knitr::include_graphics("sushi_figure1.pdf", dpi = 300) -->
<!-- ``` -->

```{=tex}
% Place figure captions after the first paragraph in which they are cited.
\begin{figure}[!h]
\caption{The figure from the batch execution of PaperFigure.R inside a Docker container generated by rang}
\label{fig2}
\end{figure}
```
